\chapter{Conclusion}

In this thesis, I addressed the challenge in the retail business: the significance of location in determining success. I began by acknowledging that location prevails in the success of a business. Historically, decisions regarding business locations relied heavily on intuition and subjective assessments, often considered more of an "art" than a science.

Recognizing the limitations of such subjective approaches, especially in the face of evolving information systems and data analytics, I set out to develop a systematic solution. The aim of this thesis was to empower retailers with a comprehensive methodology for making informed location decisions, utilizing data analysis capabilities and geographic information system (GIS) technologies.

Drawing inspiration from notable methodologies outlined in academic literature, particularly the approach proposed by \cite{roig2013retail}, I developed a system adapted to the needs of retailers. This system was designed to simplify the location decision-making process by integrating multiple datasets, utilizing GIS capabilities, and incorporating user preferences.

Throughout the work on this thesis, I have carefully created a framework for the development and implementation of this system. I have delved into the theoretical foundations of retail location assessment, studied the intricacies of GIS technologies, identified the target audience and functional requirements, studied existing solutions, and designed the interface and functionality of the system.

Having established a solid foundation, I implemented the system using advanced technologies. Extensive testing was conducted to ensure that the system was reliable, performant and compatible with real data.

Looking to the future, I see this system being used by retailers not only in the city of Brno but also in various urban landscapes around the world. By making this tool available in a public repository, I hope to enable retailers of all sizes to thrive in a competitive marketplace.

Furthermore, at the recent Excel Fit 2024 conference, this project stood out among innovative solutions, scoring an impressive 41 points. It caught the attention of attendees, who recognized its potential to transform location decision-making in retail \cite{excel2024fit}.